\textit{Supplemental figures for}: A Gaussian process model of human electrocorticographic data

### 2020-01-21 paper/supporting_information.tex
updates to paper

\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{newfloat}
\usepackage{setspace}
%\doublespacing

@@

\bibliographystyle{apa}

@@

@@

\setcounter{equation}{0}
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{page}{1}
\setcounter{section}{0}
\makeatletter
\renewcommand{\theequation}{S\arabic{equation}}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\bibnumfmt}[1]{[S#1]}
\renewcommand{\citenumfont}[1]{S#1}

@@

\bibliography{CDL-bibliography/memlab}
\bibliographystyle{CSE}
% \newpage
% \renewcommand{\refname}{Supplemental references}
% \bibliography{memlab}

>>>>

\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{newfloat}
\usepackage{setspace}
%\doublespacing

@@

%\bibliographystyle{apa}

@@

\setcounter{equation}{0}
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{page}{1}
\setcounter{section}{0}
\makeatletter
\renewcommand{\theequation}{S\arabic{equation}}
\renewcommand{\thefigure}{S\arabic{figure}}

@@

@@

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_7}
\caption{\textbf{Stability of correlation matrix across time.} \textbf{A.--B.  Features from
    Dataset 1.}  Features include: (\textbf{A. Correlation of split
  halves by the percent samples included.})  For each patient, we
  split the timeseries data in
  half and created a correlation matrix with one half.  With the
  remaining data, we created the second correlation matrix with more
  and more time samples (in 1000 sample increments).  These time
  samples were either drawn randomly (``Random'') , or were drawn sequentially from
  either the closest timepoint (``Close'' ) or the furthest timepoint
  (``Apart'' ). The two correlation matrices were then correlated, and the
  coefficient plotted relative to the percentage of data included.  (\textbf{B. Correlation of split
  halves by the number of time samples included.})
Same analysis as Panel A, but the
  coefficient plotted relative to the total number of samples included.
  \textbf{C.--D. Features from Dataset 2.}  Analogous format to Panels
  A--B.}
\label{fig:supplemental_7}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_8}
\caption{\textbf{Stability of correlation matrix across patients.} \textbf{A.--B.  Features from
    Dataset 1.}  Features include: (\textbf{A. Correlation of split
  halves by number of patients included.})  For 500 iterations, we randomly split the
patient-specific correlations in half, then created one correlation
matrix with the first half and created the second correlation matrix
using more and more patients. The two correlation matrices were then correlated, and the
  coefficient plotted relative to the number of patients included.
  (\textbf{B. Standard error of the mean across iterations by the
    number of patients included.})
To measure the variability across the iterations, we plot the standard
error of the mean as a function of the number of patients included in
the second correlation matix.  
  \textbf{C.--D. Features from Dataset 2.}  Analogous format to Panels
  A--B.}
\label{fig:supplemental_8}
\end{figure}

\renewcommand{\bibnumfmt}[1]{[S#1]}
\renewcommand{\citenumfont}[1]{S#1}
\bibliography{CDL-bibliography/memlab}
\bibliographystyle{CSE}
% \newpage
% \renewcommand{\refname}{Supplemental references}
% \bibliography{memlab}
